A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading

### 2020-09-29 paper.tex
Apply new template and add author information

\documentclass[conference]{IEEEtran}

@@

\title{A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading}
% Chinese title: 針對物聯網資料交易的去中心化基礎建設

\author{
\IEEEauthorblockN{Anonymous}
\IEEEauthorblockA{
         \textit{Anonymous Organization}\\
        ***@***.***}
%\author{\IEEEauthorblockN{1\textsuperscript{st} Ching-Hua (Vivian) Lin}
%\IEEEauthorblockA{\textit{dept. of CSIE} \\
%\textit{National Cheng Kung University}\\
%Tainan City, Taiwan (R.O.C.) \\
%jkrvivian@gmail.com}
%\and
%\IEEEauthorblockN{2\textsuperscript{nd} Ching-Chun (Jim) Huang}
%\IEEEauthorblockA{\textit{dept. of CSIE} \\
%\textit{National Cheng Kung University}\\
%Tainan City, Taiwan (R.O.C.) \\
%jserv@ccns.ncku.edu.tw}
%\and
%\IEEEauthorblockN{3\textsuperscript{rd} Chia-Heng Tu}
%\IEEEauthorblockA{\textit{dept. of CSIE} \\
%\textit{National Cheng Kung University}\\
%Tainan City, Taiwan (R.O.C.) \\
%chiaheng@gmail.com}
}

>>>>

\documentclass[10pt, conference, compsocconf]{IEEEtran}

@@

\title{A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading}

\author{\IEEEauthorblockN{Ching-Hua (Vivian) Lin}
\IEEEauthorblockA{dept. of CSIE\\
National Cheng Kung University\\
Tainan City, Taiwan (R.O.C.)\\
jkrvivian@gmail.com}
\and
\IEEEauthorblockN{Ching-Chun (Jim) Huang}
\IEEEauthorblockA{dept. of CSIE\\
National Cheng Kung University\\
Tainan City, Taiwan (R.O.C.)\\
jserv@ccns.ncku.edu.tw}
\and
\IEEEauthorblockN{Yang-Hao Yuan}
\IEEEauthorblockA{BiiLabs Co., Ltd.\\
Taiwan (R.O.C.)\\
<yanghau@biilabs.io>}
\and
\IEEEauthorblockN{Zih-shiuan (Spin) Yuan}
\IEEEauthorblockA{BiiLabs Co., Ltd.\\
Taiwan (R.O.C.)\\
<spin@biilabs.io>}
}
